### 2021-12-10 README.Rmd
update 2021-12-10 17:54:22

You can cite pema using the following citation (please use the same citation for either the package, or the paper):

> Caspar J van Lissa and Sara J van Erp (2021). pema: Penalized Meta-Analysis. R package version
0.1.0.9000. https://github.com/cjvanlissa/pema

>>>>

The `pema` validation paper is currently in preprint stage.
The code and results of the validation study are publicly available.
You can cite `pema` using the following citation (please use the same citation for either the package, or the paper); consider updating that citation once the preprint is published:

> Van Lissa, C. J., & van Erp, S. (2021, December 9). Select relevant moderators using Bayesian regularized meta-regression. Retrieved from psyarxiv.com/6phs5

### 2021-12-10 paper/manuscript.Rmd
update 2021-12-10 17:54:22

---
title             : "Select relevant moderators in meta-regression using Bayesian penalization"
shorttitle        : "BAYESIAN REGULARIZED META-ANALYSIS"

@@

abstract: |
  Todo

>>>>

---
title             : "Select relevant moderators using Bayesian regularized meta-regression"
shorttitle        : "BAYESIAN REGULARIZED META-REGRESSION"

@@

abstract: |
  When analyzing a heterogeneous body of literature, there may be many
  potentially relevant between-studies differences. These differences can be
  coded as moderators, and accounted for using meta-regression. However, many
  applied meta-analyses lack the power to adequately account for multiple
  moderators, as the number of studies on any given topic is often low. The
  present study introduces Bayesian Regularized Meta-Analysis (BRMA), an
  exploratory algorithm that can select relevant moderators from a larger number
  of candidates. This approach is suitable when heterogeneity is suspected, but
  it is not known which moderators most strongly inﬂuence the observed effect
  size. We present a simulation study to validate the performance of BRMA
  relative to state-of-the-art meta-regression (RMA). Results indicated that
  BRMA compared favorably to RMA on three metrics: predictive performance,
  which is a measure of the generalizability of results, the ability to reject
  irrelevant moderators, and the ability to recover population parameters with
  low bias. BRMA had slightly lower ability to detect true effects of relevant
  moderators, but the overall proportion of Type I and Type II errors was
  equivalent to RMA. Furthermore, BRMA regression coefficients were slightly
  biased towards zero (by design), but its estimates of residual heterogeneity
  were unbiased. BRMA performed well with as few as 20 studies in the training
  data, suggesting its suitability as a small sample solution. We discuss how
  applied researchers can use BRMA to explorate between-studies heterogeneity
  in meta-analysis.
